### 2021-06-14 paper/report.tex
Add Janos' comments on the report.

Since early 2020, the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many
months---and often years---away from reaching vaccination-induced herd immunity
\citep{Swaminathan2021}.\comment[id=HM]{Need to find some more scientific citation
before submission} In the meantime, it is of utmost importance to employ an effective
mix of strategies for containing the virus. The most frequent initial response was a set
of non-pharmaceutical interventions (NPIs) to reduce contacts between individuals. While
this has allowed some countries to sustain equilibria with very low infection
numbers\footnote{See \citet{Contreras2021} for a theoretical equilibrium at low case
numbers which is sustained with test-trace-and-isolate policies.}, most have seen large
fluctuations of infection rates over time. Containment measures have become increasingly
diverse and now include testing, more nuanced NPIs, and contact tracing. Neither these
policies' effect nor the influence of seasonal patterns or more infectious virus strains
are well understood in quantitative terms.

@@

We include two types of tests. Polymerase chain reaction (PCR) tests directly reveal
whether an individual is infected or not. PCR tests require some days to be processed
and there are aggregate capacity constraints throughout. In contrast, rapid antigen
tests yield immediate results; after a phase-in period, all tests that are demanded will
be performed. Specificity and sensitivity of these tests is set according to data
analyzed in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of the
test relative to the start of infectiousness. Figure~\ref{fig:antigen_tests} shows our
model for rapid test demand. Schools may require students to be tested regularly. Rapid
tests may be offered by employers for on-site workers. Individuals may demand tests for
private reasons, which include having plans to meet other people\footnote{A positive
    test will make them reduce their contacts; this is why tests impact the actual contacts
    in Figure~\ref{fig:model-description}.}, showing symptoms of CoViD-19, and because a
household member tested positively for the virus. We endow each agent with an individual
compliance parameter. This parameter determines whether she takes up rapid tests offered
by employers or follows up on private reasons and whether she reduces her contacts if
she tests positive or develops symptoms. The thresholds are higher for tests in a
private setting than for tests at the workplace until mid April and then compliance
because of private reasons becomes higher than compliance at the workplace.

@@

The free parameters are the infection probabilities by contact type, see Supplementary
Material~\ref{subsec:infection_probs}. We estimate these parameters so that  simulated
infections by age predict the corresponding time series in the data \citep[See][for the
general method]{McFadden1989}. However, the two sets of time series are not comparable
directly because not all cases will be recorded. We thus model recorded cases as depicted
in Figure~\ref{fig:model_for_official_cases}. We take aggregate estimates of the share of
recorded cases and use data on whether the reason for a PCR test were symptoms of
CoViD-19 to get age-specific shares. For example,\comment[id=HM]{@Janos, please correct
if necessary and insert reference} estimate unknown cases to be twice as high for
children as for adults. Confirmation of a positive rapid test result is another reason
for PCR tests, once these become available.

@@

We draw simulated samples of agents from the distribution of recorded infections in
September 2020 and use the model to predict recorded infection rates until the end of
May 2021. See Supplementary Materials~\ref{sec:data_and_parameters} and \ref{sec:model}
for detailed descriptions of the data and the model, respectively. The blue line in
Figure~\ref{fig:aggregated_fit} shows our model's predictions are very close to
officially recorded cases in the aggregate. This is also true for infections by age and
geographical region, which are shown in the supplementary materials
(Figures~\ref{fig:age_group_fit} and \ref{fig:state_fit}, respectively).

@@

In order to better understand the contributions  of rapid tests, vaccinations, and of
seasonality on the evolution of infections in 2021,
Figure~\ref{fig:2021_scenarios_broad} considers various scenarios. NPIs are always the
same as in the baseline scenario. Figure~\ref{fig:2021_scenarios_recorded} shows the
model fit (the blue line, same as in Figure~\ref{fig:aggregated_fit}), a scenario
without any of the three factors (red line), and three scenarios turning these factors
off one by one. Figure~\ref{fig:2021_scenarios_newly_infected} does the same for total
infections in the model. Figure~\ref{fig:2021_scenarios_decomposition} employs Shapley
values \citep{Shapley2016} to decompose the difference in total infections
between the scenario without any of the three factors and our main specification.

@@

Despite these large effects, the results on testing likely understate the benefits.
Disadvantaged groups of the population are less likely to be reached by testing
campaigns;\comment[id=HM]{seems obvious, but I did not find anything. COSMO data? We
should get the raw data, btw.} at the same time they have a higher risk to contract
CoViD-19.\citet{KochInstitut2021a} Mandatory tests at school and at the workplace will
extend more into these groups. The same goes for individuals who exhibit a low level of
compliance with CoViD-19-related regulations. Our analysis has shown that in the
transition path to high levels of vaccination and possibly thereafter, large-scale rapid
testing can substitute for some NPIs. This comes at a fraction of the cost. A day of the
winter lockdown in Germany is estimated to have cost 6.25~billion~Euros
\citep{Dorn2020b}.\comment[id=K]{This is a prediction by the ifo Instute back from March
2020 assuming a 2 month lockdown. I did not find anything citable that is more recent. I did
find
\href{https://www.merkur.de/wirtschaft/lockdown-coronavirus-kosten-deutschland-milliarden-euro-wirtschaft-krise-zr-90231189.html}{A
quote from ifo's Timo Wollmershäuser: „Wir liegen zwischen zwei bis zweieinhalb
Milliarden Euro pro Woche“} for the winter lockdown. That would be much less than calculated in March.} In early June 2021, retail prices
for self-administered rapid tests are frequently less than 1.5~Euro.\footnote{Cheapest on
\href{https://amazon.de}{Amazon} on June 11th, 2021.}

>>>>

Since early 2020,\comment[id=J]{\textbf{Features that are not highlighted enough:}

\begin{itemize}
    \item Low sensitivity of rapid tests before and on day of infectiousness onset
    \item Different seasonalities for different contact types (and quite strong for other contacts)
    \item Low number of breakpoints in parameters / policies compared to breakpoints in
    cases / reproduction rate
\end{itemize}

} the CoViD-19 pandemic has presented an enormous challenge to humanity
on many dimensions. The development of highly effective vaccines holds the promise of
containment in the medium term. However, most countries find themselves many
months---and often years---away from reaching vaccination-induced herd immunity
\citep{Swaminathan2021}.\comment[id=HM]{Need to find some more scientific citation
before submission} In the meantime, it is of utmost importance to employ an effective
mix of strategies for containing the virus. The most frequent initial response was a set
of non-pharmaceutical interventions (NPIs) to reduce contacts between individuals. While
this has allowed some countries to sustain equilibria with very low infection
numbers\footnote{See \citet{Contreras2021} for a theoretical equilibrium at low case
numbers which is sustained with test-trace-and-isolate policies.}, most have seen large
fluctuations of infection rates over time. Containment measures have become increasingly
diverse and now include testing, more nuanced NPIs, and contact tracing. Neither these
policies' effect nor the influence of seasonal patterns or more infectious virus strains
are well understood in quantitative terms.

@@

We include two types of tests. Polymerase chain reaction (PCR) tests
directly\comment[id=J]{It is not clear what "directly" means} reveal whether an
individual is infected or not. PCR tests require some days to be processed and there are
aggregate capacity constraints throughout. In contrast, rapid antigen tests yield
immediate results; after a phase-in period, all tests that are demanded will be
performed. Specificity and sensitivity of these tests is set according to data analyzed
in \cite{Bruemmer2021, Smith2021}; sensitivity depends on the timing of the test relative
to the start of infectiousness. Figure~\ref{fig:antigen_tests} shows our model for rapid
test demand. Schools may require students to be tested regularly. Rapid tests may be
offered by employers for on-site workers. Individuals may demand tests for private
reasons, which include having plans to meet other people\footnote{A positive test will
make them reduce their contacts; this is why tests impact the actual contacts in
Figure~\ref{fig:model-description}.}, showing symptoms of CoViD-19, and because a
household member tested positively for the virus. We endow each agent with an individual
compliance parameter. This parameter determines whether she takes up rapid tests offered
by employers or follows up on private reasons and whether she reduces her contacts if she
tests positive or develops symptoms. The thresholds are higher for tests in a private
setting than for tests at the workplace until mid April and then compliance because of
private reasons becomes higher than compliance at the workplace.\comment[id=J]{Shouldn't
we mention that this is because of availability / high costs?}

@@

The free parameters are the infection probabilities by contact type, see Supplementary
Material~\ref{subsec:infection_probs}. We estimate these parameters so that simulated
infections by age predict the corresponding time series in the data \citep[See][for the
general method]{McFadden1989}. However, the two sets of time series are not comparable
directly because not all cases will be recorded. We thus model recorded cases as depicted
in Figure~\ref{fig:model_for_official_cases}. We take aggregate estimates of the share of
recorded cases and use data on whether the reason for a PCR test were symptoms of
CoViD-19 to get age-specific shares. For example,\comment[id=HM]{@Janos, please correct
if necessary and insert reference} estimate unknown cases to be twice as high for
children as for adults. Confirmation of a positive rapid test result is another reason
for PCR tests, once these become available.\comment[id=J]{Free parameters also include:

- One hygiene multiplier for school an work contacts after November 2
- A few "other" multipliers including two lockdown fatigue effects
- Number of extra contacts during holidays

Strictly speaking also:
- The fade in speed of the rapid tests
- Share known cases around holidays }

@@

We draw simulated samples of agents from the distribution of recorded infections in
September 2020 and use the model to predict recorded infection rates until the end of May
2021.\comment[id=J]{I do not understand} See Supplementary
Materials~\ref{sec:data_and_parameters} and \ref{sec:model} for detailed descriptions of
the data and the model, respectively. The blue line in Figure~\ref{fig:aggregated_fit}
shows our model's predictions are very close to officially recorded cases in the
aggregate. This is also true for infections by age and geographical region, which are
shown in the supplementary materials (Figures~\ref{fig:age_group_fit} and
\ref{fig:state_fit}, respectively).

@@

In order to better understand the contributions  of rapid tests, vaccinations, and of
seasonality on the evolution of infections in 2021, Figure~\ref{fig:2021_scenarios_broad}
considers various scenarios. NPIs are always the same as in the baseline scenario.
Figure~\ref{fig:2021_scenarios_recorded} shows the model fit (the blue line, same as in
Figure~\ref{fig:aggregated_fit}), a scenario without any of the three factors (red line),
and three scenarios turning these factors off one by one.
Figure~\ref{fig:2021_scenarios_newly_infected} does the same for total infections in the
model. Figure~\ref{fig:2021_scenarios_decomposition} employs Shapley values
\citep{Shapley2016} to decompose the difference in total infections between the scenario
without any of the three factors and our main specification.\comment[id=J]{I would not
mention the word "coalition" in the notes to the figure on the Shapley values.
Combination with other channels is better. I think I would prefer to have a short section
on shapley values in the appendix (why use them, how do they work) and just link to that
in the figure note}

@@

Despite these large effects, the results on testing likely understate the benefits.
Disadvantaged groups of the population are less likely to be reached by testing
campaigns;\comment[id=HM]{seems obvious, but I did not find anything. COSMO data? We
should get the raw data, btw.} at the same time they have a higher risk to contract
CoViD-19.\citet{KochInstitut2021a} Mandatory tests at school and at the workplace will
extend more into these groups. The same goes for individuals who exhibit a low level of
compliance with CoViD-19-related regulations.

Our analysis\comment[id=J]{The conclusion should be slightly longer and more separated from the rest} has shown that in the transition path to high levels of vaccination and
possibly thereafter, large-scale rapid testing can substitute for some NPIs. This comes
at a fraction of the cost. A day of the winter lockdown in Germany is estimated to have
cost 6.25~billion~Euros \citep{Dorn2020b}.\comment[id=K]{This is a prediction by the ifo
Instute back from March 2020 assuming a 2 month lockdown. I did not find anything citable
that is more recent. I did find
\href{https://www.merkur.de/wirtschaft/lockdown-coronavirus-kosten-deutschland-milliarden-euro-wirtschaft-krise-zr-90231189.html}{A
quote from ifo's Timo Wollmershäuser: „Wir liegen zwischen zwei bis zweieinhalb
Milliarden Euro pro Woche“} for the winter lockdown. That would be much less than
calculated in March.} In early June 2021, retail prices for self-administered rapid tests
are frequently less than 1.5~Euro.\footnote{Cheapest on \href{https://amazon.de}{Amazon}
on June 11th, 2021.}
